Title of the Master Thesis

### 2015-10-20 Master Thesis/synopsis.tex
Use group operation notation
Finalize chapter 1

\begin{remark}
If $L\subset M$ are intermediate fields of $\overline{K}/K$, which are finite over $K$, then $\sigma$ also induces bijections
\[ \operatorname{Spv}_\text{d}^{(1)}(L) \to \operatorname{Spv}_\text{d}^{(1)}(L'),\qquad \operatorname{Spv}_\text{d}^{(1)}(M) \to \operatorname{Spv}_\text{d}^{(1)}(M') \]
such that the following diagram commutes:
\[\begin{tikzcd}
\operatorname{Spv}_\text{d}^{(1)}(M) \rar["\sigma"]\dar & \operatorname{Spv}_\text{d}^{(1)}(M')\dar\\
\operatorname{Spv}_\text{d}^{(1)}(L) \rar["\sigma"'] & \operatorname{Spv}_\text{d}^{(1)}(L')
\end{tikzcd}\]
where the vertical maps are restrictions. Let $w\in\operatorname{Spv}_\text{d}^{(1)}(M),\ v=w|_L$ and $w'=\sigma(w),\ v'=\sigma(v)$. Then the following diagram commutes:
\[ \begin{tikzcd}
k(w') \rar["\varphi_w"] & k(w)\\
k(v') \rar["\varphi_v"']\uar[hook] & k(v)\uar[hook]
\end{tikzcd} \]
By a limit process we see that $\sigma$ induces a bijection $\sigma: \operatorname{Spv}_\text{d}^{(1)}(\overline{K})\to \operatorname{Spv}_\text{d}^{(1)}(\overline{K'})$. Let $\overline{v}\in \operatorname{Spv}_\text{d}^{(1)}(\overline{K})$ and $G_{\overline{v}}\subset G_K$ be the decomposition group of $\overline{v}$. Then we have $\sigma(G_{\overline{v}}) = G_{\sigma(\overline{v})}$. Now it is easy to see that for every $g\in G_K$:
\[ \sigma(\overline{v}\circ g) = \sigma(\overline{v})\circ \sigma(g) \]
\end{remark}

@@

Let $T_1, T_2\subset X_0\setminus S$ be two $S$-admissible subsets and suppose $T_1\subset T_2$. By observing $(\star)$ we find:
\[ r_{S,T_1}\circ\varphi^{S,T_2}=\Big(\prod_{P\in T_1}\varphi_P\Big)\circ r_{S',T_1'} = r_{S,T_1}\circ\varphi^{S,T_1} \]
Since $r_{S,T_1}$ is injective we get $\varphi^{S,T_2}=\varphi^{S,T_1}$. Hence, $\varphi^{S,T}$ is actually independent of $T$, thus we can omit the $T$ from its notation. Now, if $T$ ranges over all $S$-admissible subsets of $X_0$, then $(\star)$ shows:
\[ r_S\circ\varphi^S = \Big(\prod_{P\in X_0\setminus S}\varphi_P \Big)\circ r_{S'} \]
In other words, we can replace $T$ by $X_0\setminus S$ in $(\star)$. If $S_1\subset S_2$ are two admissible subsets, then:
\[ r_{S_2}\circ\varphi^{S_2}|_{K'^{S'_1}} = \Big(\prod_{P\in X_0\setminus S_2}\varphi_P \Big)\circ r_{S'_2}|_{K'^{S'_1}} = r_{S_2}\circ\varphi^{S_1} \]
Hence, $\varphi^{S_1}=\varphi^{S_2}|_{K'^{S'_1}}$. Thus, we can combine the isomorphisms $\varphi^S$, where $S$ ranges over the admissible subsets of $X_0$, into an isomorphism $\varphi = \varinjlim \varphi^S: K'^\times \to K^\times$. Note that for every $x\in K^\times$ we have $v_P(x)\neq 0$ for finitely many $P\in X_0$; similarly for $K'$ and $X'_0$. $\varphi$ has the desired properties.
\end{proof}

@@

\begin{step}
$\varphi$ induces $\sigma:G_K\to G_{K'}$, i.e. $\sigma(g) = \varphi^{-1}g\varphi$ for all $g\in G_K$, and is uniquely determined by this property.
\end{step}

>>>>

\begin{remark}
If $L\subset M$ are intermediate fields of $\overline{K}/K$, which are finite over $K$, then $\sigma$ also induces bijections
\[ \operatorname{Spv}_\text{d}^{(1)}(L) \to \operatorname{Spv}_\text{d}^{(1)}(L'),\qquad \operatorname{Spv}_\text{d}^{(1)}(M) \to \operatorname{Spv}_\text{d}^{(1)}(M') \]
such that the following diagram commutes:
\[\begin{tikzcd}
\operatorname{Spv}_\text{d}^{(1)}(M) \rar["\sigma"]\dar & \operatorname{Spv}_\text{d}^{(1)}(M')\dar\\
\operatorname{Spv}_\text{d}^{(1)}(L) \rar["\sigma"'] & \operatorname{Spv}_\text{d}^{(1)}(L')
\end{tikzcd}\]
where the vertical maps are restrictions. Let $w\in\operatorname{Spv}_\text{d}^{(1)}(M),\ v=w|_L$ and $w'=\sigma(w),\ v'=\sigma(v)$. Then the following diagram commutes:
\[ \begin{tikzcd}
k(w') \rar["\varphi_w"] & k(w)\\
k(v') \rar["\varphi_v"']\uar[hook] & k(v)\uar[hook]
\end{tikzcd} \]
By a limit process we see that $\sigma$ induces a bijection $\sigma: \operatorname{Spv}_\text{d}^{(1)}(\overline{K})\to \operatorname{Spv}_\text{d}^{(1)}(\overline{K'})$. Let $\overline{v}\in \operatorname{Spv}_\text{d}^{(1)}(\overline{K})$ and $G_{\overline{v}}\subset G_K$ be the decomposition group of $\overline{v}$. Then we have $\sigma(G_{\overline{v}}) = G_{\sigma(\overline{v})}$. Now it is easy to see that for every $g\in G_K$:
\[ \sigma(g\overline{v}) = \sigma(g)\sigma(\overline{v}) \]
\end{remark}

@@

Let $T_1, T_2\subset X_0\setminus S$ be two $S$-admissible subsets and suppose $T_1\subset T_2$. By observing $(\star)$ we find:
\[ r_{S,T_1}\circ\varphi^{S,T_2}=\Big(\prod_{P\in T_1}\varphi_P\Big)\circ r_{S',T_1'} = r_{S,T_1}\circ\varphi^{S,T_1} \]
Since $r_{S,T_1}$ is injective we get $\varphi^{S,T_2}=\varphi^{S,T_1}$. Hence, $\varphi^{S,T}$ is actually independent of $T$, thus we can omit the $T$ from its notation. Now, if $T$ ranges over all $S$-admissible subsets of $X_0$, then $(\star)$ shows:
\[ r_S\circ\varphi^S = \Big(\prod_{P\in X_0\setminus S}\varphi_P \Big)\circ r_{S'} \]
In other words, we can replace $T$ by $X_0\setminus S$ in $(\star)$. If $S_1\subset S_2$ are two admissible subsets, then:
\[ r_{S_2}\circ\varphi^{S_2}|_{K'^{S'_1}} = \Big(\prod_{P\in X_0\setminus S_2}\varphi_P \Big)\circ r_{S'_2}|_{K'^{S'_1}} = r_{S_2}\circ\varphi^{S_1} \]
Hence, $\varphi^{S_1}=\varphi^{S_2}|_{K'^{S'_1}}$. Thus, we can combine the isomorphisms $\varphi^S$, where $S$ ranges over the admissible subsets of $X_0$, into an isomorphism $\varphi = \varinjlim \varphi^S: K'^\times \to K^\times$. Note that for every $x\in K^\times$ we have $v_P(x)= 0$ for almost all $P\in X_0$; similarly for $K'$ and $X'_0$.

Now note that for any $x\in U_{P'}$ we can find an admissible set $S\subset X_0\setminus \{P\}$ such that $x\in K'^{S'}$.
\end{proof}

@@

\begin{step}
$\varphi$ induces $\sigma:G_K\to G_{K'}$, i.e. $\sigma(g) = \varphi^{-1}\circ g\circ \varphi$ for all $g\in G_K$, and is uniquely determined by this property.
\end{step}

\begin{proof}
Let $\tau:G_K\to G_{K'},\ g\mapsto \varphi^{-1}\circ g\circ \varphi$. Clearly, $\tau$ is a group isomorphism and we have $\tau(G_L)=G_{L'}=\sigma(G_L)$ for every finite subextension $L/K$ of $\overline{K}/K$. By Lemma \ref{3.2}, $\tau$ induces bijections $\tau: \operatorname{Spv}_\text{d}^{(1)}(L)\to \operatorname{Spv}_\text{d}^{(1)}(L')$ for any intermediate field $L$ of $\overline{K}/K$.
\end{proof}
